---
title: "Worker Script Report: Populate Cipit Tables"
author: "Monica Gucciardi"
date: "`r lubridate::now()`"
output: html_document
---

```{r setup, include=FALSE}
#database packages
library(odbc)
library(pool)

#data manipulation packages
library(tidyverse)

#hashing packages
library(digest)

#Other stuff
library(knitr)
options(stringsAsFactors = FALSE)

# ODBC Connection to CIPIT
cipit <- dbConnect(odbc(),
    Driver = "SQL Server", 
    Server = "PWDCIPSQLR", 
    Database = "CIPITREADER", 
    uid = Sys.getenv("cipit_uid"),
    pwd= Sys.getenv("cipit_pwd"))

# ODBC Connection to MARS
mars <- dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "mars_prod",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)

log_code <- digest(now()) #Unique ID for the log batches

errorCodes <- data.frame(code = 0:3,
  message = c("Execution successful.",
              "Could not connect to DB. Is Postgres or CIPIT down?",
              NA, #Write error from TryCatch will be used
              NA #Write error from TryCatch will be used
              ), stringsAsFactors=FALSE)

kill = FALSE
success = FALSE
errorCode = 0

  ###Log: Start
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = 1,
                           exit_code = NA,
                           note = "Testing DB Connection")
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)


  #################################
  ####Error check - Did we connect?
  #################################
  if(any(typeof(mars) == "list", !odbc::dbIsValid(cipit)))
  {
    kill = TRUE
    errorCode = 1
  }
```

```{r Break Point 1 - Bad Connection, echo = FALSE, eval = kill}

  knitr::asis_output("# Script Results: Error\n")
  knitr::asis_output(paste("## Error Code:", errorCode, "\n"))
  knitr::asis_output(paste("## Error Message: ", errorCodes$message[errorCode+1]))
  
  ###Log: End
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = NA,
                           exit_code = errorCode,
                           note = errorCodes$message[errorCode+1])
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)
  
  knitr::knit_exit()

```

## Worker Script Report: Populate CIPIT Tables

This script is attempting to connect to the database `CIPITREADER` on the `PWDCIPSWLR` server. Once connected, the script will query data from `CIPITREADER`, hash rows of data, and compare the hashes from `CIPITREADER` to those stored on `mars_data`.

```{r Section 1 - Querrying and Hashing, echo = FALSE, include = FALSE}
  ###Log: Start
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = 2,
                           exit_code = NA,
                           note = "Querying CIPIT")
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)

cipit_project_query <- 'select _Work_Number as worknumber, _Project_Phase as project_phase, _Project_Phase_Status as project_phase_status, _Project_Title as project_title, _Targeted_Bid_FY as targeted_bid_fy, PC_NTP_Date as pc_ntp_date, CONST_Construction_Start_Date as construction_start_date, DESIGN_Design_Engineer as design_engineer, CONST_Division_Engineer as division_engineer, CONST_Contractor as contractor, ProjectAutoID as projectautoid, CONST_Substantially_Complete_Date as construction_complete_date, CONST_Contract_Close_Date as contract_closed_date from Project'
cipit_project <- dbGetQuery(cipit, cipit_project_query)

cipit_project$targeted_bid_fy <- as.numeric(cipit_project$targeted_bid_fy)

cipit_project_hash <- cipit_project %>%
    unite("temp", remove = FALSE) %>%
    rowwise() %>%
    mutate(md5hash = digest(temp, algo = 'md5')) %>%
    select(-temp)

cipit_project_db <- dbGetQuery(mars, "select * from external.tbl_cipit_project")

cipit_project_anti <- anti_join(cipit_project_hash, cipit_project_db, by = "md5hash")
cipit_project_new <- filter(cipit_project_anti,!(worknumber %in% cipit_project_db$worknumber))

cipit_project_update = anti_join(cipit_project_anti, cipit_project_new, by = "md5hash") %>%
    left_join(select(cipit_project_db, cipit_project_uid, worknumber))
```

```{r Section 2 - Comparing Databases and Writing to Databases, echo = FALSE, eval = all(!kill, nrow(cipit_project_new) > 0)}
knitr::asis_output(paste0("### CIPIT contains ", nrow(cipit_project_new), " new projects."))
kable(head(cipit_project_new))

  ###Log: Start
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = 3,
                           exit_code = NA,
                           note = "Writing New Data")
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)

tryCatch(

  expr = {
    dbWriteTable(mars, 
      RPostgres::Id(schema = "external", table = "tbl_cipit_project"), 
      cipit_project_new, 
      append= TRUE, 
      row.names = FALSE)
    success <<- TRUE
    },
  error = function(e) {
    kill <<- TRUE
    errorCode <<- 2
    errorCodes$message[errorCode+1] <<- e$message #Error object is a list
  }
)
  
if(!kill){
    #Writing file counts
    logMessage <- data.frame(date = as.Date(today()),
                         records = nrow(cipit_project_new),
                         type = "Records",
                         hash = log_code)

    dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_writes_cipit"), logMessage, append = TRUE, row.names=FALSE)
}

```

```{r Break Point 2 - Bad Write, echo = FALSE, eval = kill}

  knitr::asis_output("# Script Results: Error\n")
  knitr::asis_output(paste("## Error Code:", errorCode, "\n"))
  knitr::asis_output(paste("## Error Message: ", errorCodes$message[errorCode+1]))
  
  ###Log: End
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = NA,
                           exit_code = errorCode,
                           note = errorCodes$message[errorCode+1])
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)
  
  knitr::knit_exit()

```

```{r Section 3: Updating existing records, echo = FALSE, eval = all(!kill, nrow(cipit_project_update) > 0)}
knitr::asis_output(paste0("### CIPIT contains ", nrow(cipit_project_update), " updated projects."))
kable(head(cipit_project_update))

  ###Log: Start
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = 4,
                           exit_code = NA,
                           note = "Updating changed data")
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)

tryCatch(

  expr = {
      purgeQuery <- paste0("delete from external.tbl_cipit_project where cipit_project_uid in (", paste(cipit_project_update$cipit_project_uid, collapse = ", "), ");")
      dbExecute(mars, purgeQuery)
      dbWriteTable(mars, RPostgres::Id(schema = "external", table = "tbl_cipit_project"), cipit_project_update, append = TRUE)
      success <<- TRUE
    },
  error = function(e) {
    kill <<- TRUE
    errorCode <<- 3
    errorCodes$message[errorCode+1] <<- e$message #Error object is a list
  }
)
  
if(!kill){
    #Writing file counts
    logMessage <- data.frame(date = as.Date(today()),
                         records = nrow(cipit_project_update),
                         type = "Updates",
                         hash = log_code)

    dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_writes_cipit"), logMessage, append = TRUE, row.names=FALSE)
}
    

```

```{r Break Point 3 - Bad Update, echo = FALSE, eval = kill}

  knitr::asis_output("# Script Results: Error\n")
  knitr::asis_output(paste("## Error Code:", errorCode, "\n"))
  knitr::asis_output(paste("## Error Message: ", errorCodes$message[errorCode+1]))
  
  ###Log: End
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = NA,
                           exit_code = errorCode,
                           note = errorCodes$message[errorCode+1])
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)
  
  knitr::knit_exit()

```

# Script Results: `r ifelse(kill, "FAILURE", "SUCCESS")`
## Exit Code: `r errorCode`
## Exit Message: `r errorCodes$message[errorCode+1]`

```{r Section 3 - Close DB connections and render this file, include = FALSE}
# Close database connections

  ###Log: End
  logMessage <- data.frame(date = as.Date(today()), hash = log_code,
                           milestone = NA,
                           exit_code = errorCode,
                           note = errorCodes$message[errorCode+1])
  
  dbWriteTable(mars, RPostgres::Id(schema = "log", table = "tbl_script_cipit"), logMessage, append = TRUE, row.names=FALSE)

dbDisconnect(cipit)

```

