---
title: "SF segfault reprex"
output: html_document
date: "2025-07-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Section 0: Preamble ----
#GIS stuff
library(sf)
library(s2)

#Dplyr stuff
library(magrittr)
library(tidyverse)

#Database Stuff
library(odbc)
library(pool)

#Other stuff
library(knitr)
library(digest)
options(stringsAsFactors=FALSE)

###Section 0.1: Check parameter validity

#ODBC String for GIS DB
dsn_infra_pub <- paste0("MSSQL:server=PWDGISSQL;",
                        "database=GIS_APPS;",
                        "UID=", Sys.getenv("gis_uid"), ";",
                        "PWD=", Sys.getenv("gis_pwd"), ";")


marsDBCon <- dbPool(
  drv = RPostgres::Postgres(),
  host = "PWDMARSDBS1",
  port = 5434,
  dbname = "mars_prod",
  user= Sys.getenv("admin_uid"),
  password = Sys.getenv("admin_pwd"),
  timezone = NULL)

```

suppressWarnings hides an unrelated warning from a driver bug. It's a method Tyler endorses to interact with spatial sources via st_read
The warning is: Warning: GDAL Error 1: Error initializing the metadata tables : [37000][Microsoft][ODBC SQL Server Driver][SQL Server]CREATE TABLE permission denied in database 'GIS_APPS'

This is otherwise unrelated to the issue at hand. The following code works locally and fails on Connect with a segfault.

```{r st_read segfault when reading from a database}

  smp_loc <- dbGetQuery(marsDBCon, "SELECT * FROM admin.tbl_smp_loc")
  smp_loc$lon_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lon_wgs84
  smp_loc$lat_wgs84 %>% as.numeric %>% round(4) -> smp_loc$lat_wgs84

  bumpout <- suppressWarnings(st_read(dsn_infra_pub, "gisad.GSWIBUMPOUT", quiet = TRUE)) %>% 
    st_set_crs(2272) %>% st_transform(4326) %>% #Convert from PA State Plane to WGS 1984
    st_centroid %>% filter(!is.na(SMP_ID)) %>% transmute(smp_id = gsub("\\s", "", SMP_ID)) %>%
    filter(!(grepl("[A-z]", smp_id))) %>% #No A-Z characters permitted. Upper and lower case.
    filter(!(smp_id %in% smp_loc$smp_id)) %>%
    {data.frame(st_coordinates(.), .$smp_id)} %>%
    select(smp_id = 3, lon_wgs84 = 1, lat_wgs84 = 2)
```

